Demes: a specification for interchanging complex demography

### 2022-03-22 paper.tex
comments from jerome

Demographic models consist of one or more populations (or ``demes'') defined
by their size histories and the time intervals of their existence.
Individuals can move between populations based on their ancestor-descendant
relationships (i.e., the topology) or by continuous or discrete migration events.
The deomgraphic model itself omits information about genome biology, such as
genome size and architecture, ploidy, and mutation and recombination rates.
It also omits any information about selection operating within populations.
Within populations, allele-frequency dynamics are implicitly assumed to
follow the Wright-Fisher model, so that generations are discrete and
non-overlapping and population sizes are independent of mean fitness
(i.e., ``soft'' selection~\citep{christiansen1975hard}).
While these restrictions preclude some population-genetic scenarios of
interest, such as explicit spatial structure or
\aprcomment{stochastic carrying-capacity models, or something like that},
many current forwards- and backwards-in-time simulation software
make these same assumptions, so that Demes is relevant to a range of
widely-used simulators.
In Appendix~\ref{sec:appendix-pop-gen-model}, we expand on these concepts
and provide more details on the population genetics models supported by Demes.

>>>>

Demographic models consist of one or more populations (or ``demes'') defined
by their size histories and the time intervals of their existence.
Individuals can move between populations based on their ancestor-descendant
relationships (i.e., the topology) or by continuous or discrete migration events.
The deomgraphic model itself omits information about genome biology, such as
genome size and architecture, ploidy, and mutation and recombination rates.
It also omits any information about selection operating within populations.
Within populations, allele-frequency dynamics are assumed to
follow the Wright-Fisher model, so that generations are discrete and
non-overlapping and population sizes are independent of mean fitness
(i.e., ``soft'' selection~\citep{christiansen1975hard}).
While these restrictions preclude some population-genetic scenarios of
interest, such as continuous spatial structure
\aprcomment{citations here, and revisit} or
\aprcomment{stochastic carrying-capacity models, or something like that},
many current forwards- and backwards-in-time simulation software
make these same assumptions, so that Demes is relevant to a range of
widely-used simulators.
\jkcomment{I guess these are also the basic assumptions also shared by
inference methods, which is important. Mabye another sentence here making this
explicit, and listing a few different types of inference methods and giving
citations? This is critical - we want to establish that Demes is the
"middleware" between the inference methods and the simulators, and captures the
basic assumptions made by them all.}
In Appendix~\ref{sec:appendix-pop-gen-model}, we expand on these concepts
and provide more details on the population genetics models supported by Demes.
